The Driving Forces Behind API Evolution

### 2015-05-19 thesis/paper.tex
Quotes from Swanson and Chapin

\subsection{RQ1 Results} \label{results_rq1}
%Lehman Intro

Our analysis of the results related to \textbf{RQ2} showed that seven out of the eight laws \cite{lehman90sview} do apply to APIs. A summary of our findings can be seen in Table \ref{table:lehman}. The evidence found for the laws of continuing change, self regulation, conservation of familiarity, continuing growth and feedback system mainly relate to enhancive changes that add functionality to the API. It was also found that the laws of increasing complexity and declining quality do apply, but that the changes which support these laws usually had a secondary intent related to complexity or quality. The only law which was found not to apply to the API analysed in this study was the law of conservation of organisational stability. Our results rather show the opposite, that the work rate is variant.

In the remainder of this section we will discuss the results related to each law, and discuss if our results show that the laws apply to APIs or not.

@@

       [quotes re. communication/stakeholders]:

>>>>

\subsection{RQ1 Results} \label{results_rq1}

%Types intro
The results show that certain types of change are more prevalent than others, these results are shown in \ref{table:type_counts}. Analysis of the results showed that enhancive changes were the primary types of change that drive API evolution and that they act as a catalyst for many of the other changes in the API. Updative changes were found to be consequences of enhancive changes, rather than being drivers of evolution. Supporting the users of the API through the combination of preventive and groomative types of change, together formed another strong driver of API evolution. Reductive and adaptive changes, while important, did not strongly drive the evolution of the API. No evidence was found for corrective, performance types of change. Similarly, there was no evidence found for evaluative, consultive nor training activities.

%Lehman Intro
Our analysis of the results related to \textbf{RQ1} showed that seven out of the eight laws \cite{lehman90sview} do apply to APIs. A summary of our findings can be seen in Table \ref{table:lehman}. The evidence found for the laws of continuing change, self regulation, conservation of familiarity, continuing growth and feedback system mainly relate to enhancive changes that add functionality to the API. It was also found that the laws of increasing complexity and declining quality do apply, but that the changes which support these laws usually had a secondary intent related to complexity or quality. The only law which was found not to apply to the API analysed in this study was the law of conservation of organisational stability. Our results rather show the opposite, that the work rate is variant.

In the remainder of this section we will discuss the results related to each type of change category, discussing the results for each of them with examples from the changes identified between the two versions of the API. Subsequently, each of Lehman's laws will be discussed and our results will be presented showing if the laws apply to APIs or not.

@@

   ``Managers involved in software evolution and software maintenance have great difficulty in
   defining, justifying, budgeting, staffing, supervising, accounting for, marshalling resources
   for, and assessing the work when coarse non-objective measures are used [4]. Things not
   appropriately named are often undervalued and treated as miscellaneous or trivial, since
   communication about them is made more cumbersome.'' %Chapin

       [quotes re. communication/stakeholders]:
       ``management must be thoroughly fami-liar with the organizational conventions and practices
involved, in order to make intelligent decisions.'' //Swanson
``provide a realistic and practical classification to facilitate communication about, and the
management of, software evolution and maintenance among researchers, practitioners, and their
managers;'' //Chapin

%Whole bunch of Swanson stuff below.
% The implications for the management of software
% maintenance are several. First, insofar as maintenance
% is performed informally, i.e. in the absence of an
% established set of organizational conventions and prac-
% tices, the measurement of maintenance performance w i l l
% not be feasible. The establishment of a maintenance
% data base, a precondition to performance measurement,
% is not possible in the absense of organizational struc-
% ture. In informal situations, performance must be assessed informally.

% Secondly, in any given organization in which main-
% tenance performance is formally assessed, in terms of
% specific measures, management must be thoroughly fami-
% l i a r with the organizational conventions and practices
% involved, in order to make intelligent decisions. No
% single measure or set of measures w i l l i t s e l f reveal
% that maintenance is going "better" or "worse" than
% management has a right to expect or desire. Such a
% judgment must follow as a systemic inference from an
% analysis of the performance measurements, made in the
% context of f a m i l i a r i t y with the organizational struc-
% ture which made these measurements possible.

% Finally, in the absence of f a m i l i a r i t y with other,
% alternative organizational structures for performing
% maintenance, management w i l l be essentially unable to
% assess i t s own established structure. Nothing in the
% performance measurements made within the context of the
% established structure w i l l indicate the opportunity
% costs associated with this structure. Management must
% look outside, to the performance measurements and
% structures of other organizations, to assess what might
% reasonably be achieved through organizational change.

% In the context of a maintenance organizational
% structure and a particular set of data gathered in the
% performance of maintenance within this structure, i t
% is possible to derive some performance measures which
% should be appropriately "suggestive" to management.

% Measures of maintenance performance are
% not meaningful except within the context
% of the organizational structure(s) upon
% which they are based.
